---
title: "R Notebook"
output: html_notebook
---

# Import your data & load your R packages

```{r}

library(readr) #This allows us to import csv files
library(dplyr) #This is the data editing & wrangling package
library(ggplot2) #This is ggplot2!
export <- read_csv("export.csv")

```

# I've just exported this from qualtrics, this data is dirty!
### Some of my variable names are really long, and not 1 word
### My date is not formatted as a date
### All my discrete variables are characters, I want them to be factors to avoid confusion
```{r}
export
```

# Clean your data
## Feel free to do most of this in google sheets if you prefer
### Just make sure you format the data properly as a date, numeric, factor etc


```{r}

ds <- export %>% # I'm creating a new data sheet called  'ds'
  mutate(date = as.Date(.$`Recorded Date`, format = "%d/%m/%y"), # naming the `Recorded Date` variable to date, and converting the variable type to a date
         social_follow = factor(.$`Where do you follow the FT on social media?`), # naming this variable social_follow and turning it into a factor
         content_associate = factor(.$`Which of the following content do you associate with the FT? (Select any that apply) - Selected Choice`),
         three_words = .$`How would you describe the FT in three words?`,
         hold_sub = .$`Have you ever held an FT subscription?`) %>% 
  select(date, social_follow, content_associate, three_words, hold_sub) %>% #Now only selecting the data I want to analyse
  mutate(hold_sub = recode(hold_sub,
                           "I signed up for a trial offer in the past, but did not continue" = "Lapsed trialist",
                           "I used to have an FT subscription, but have since cancelled" = "Former subscriber",
                           "I'm currently an FT subscriber" = "Current subscriber",
                           "No" = "Never subscribed")) # I didn't like the long names for this factor so I renamed them into something more digestable


ds

```